### 2017-04-12 thesis/latex/thesis.tex
Thesis: minor commit.

As shown in \ref{dynein-artist-rendition-2}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.

@@

\subsubsection{How does it behave?}
Talk about its stepping behavior using Weihong's figures (as well as the new paper David found?)\\

Also possibly talk about the other things Dynein has been found to do, such as hydrolyse ATP and move its subdomains around. This may be better in a different section than the introduction though, since its a lot of biochemistry for the second section in an intro? maybe not, it has to go somewhere.

@@

@@

Side stepping of dynein is ignored in this model. Stepping perpendicular to the MT occurs in dynein \cite{weihongppaer}, as shown in Figure \ref{fig:weihong-side-stepping}. This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

@@

\section{Chapter: Results}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\

@@

\section{Chapter: Discussion}
\subsubsection{Limitations}
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy...

@@

Computational limitations: Our project is computational, not experimental. Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\

\subsection{Future work on this project}
If setbacks happen, this'll be a big section. Or, further simulations which could be done. Namely taking our model and giving it lots more states and seeing if this model even better fits experimental data.\\

\subsubsection{Experiments to verify our model}
Talk about how FRET could be used to verify our model. We have domain distance info over long
timescales in our model - this is something we could compare to a FRET experiment exploring
the distance between domains in dynein.\\

@@

Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using
vanadium? Maybe...\\
\subsection{Possible further projects}
\subsection{Difference between dynein and kinesin}
Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin?
Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This
would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility
and get its crystal structure to do some comparisons.

>>>>

As shown in the crystal structure in Figure XXX, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.

@@

This could be fixed up...probably remove multiple of these sections

\subsubsection{How does it behave?}
Dynein's stepping pattern is distinct from its partner, kinesin. Kinesin takes very precise 8-nm steps \cite{kinesin-step-size}. In contrast, dynein takes a large range of steps, as shown in Figure \\

@@

In reality, all molecules have a degree of elasticity. A dynein model by Sarlah \textit{et. al.} models the dynein stalk as an elastic rod \cite{sarlahmodel}. However, the timescale of harmonic stalk oscillations is likely much quicker than that of the mechanochemical cycle, so it is reasonable to model the stalk as a rigid rod at the stalk's average extension length.\\

@@

Side stepping of dynein is ignored in this model. Stepping perpendicular to the MT occurs in dynein \cite{weihongpaper}, as shown in Figure \ref{fig:weihong-side-stepping}. This model assumes it is a symptom, and not an influencer of, of dynein's forward-backward stepping mechanism.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

\textbf{Way to represent heatmap: show a blowup of the most promising section of the first heatmap, then a blowup of the second, etc until the optimum is found}

@@

\section{Chapter: Results \& Discussion}
\subsection{Stepping behavior of fit model}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\

@@

Our project un/successfully predicted how dynein behaved. How would we modify it to describe kinesin? Is dynein's linker-motor connection less tense than kinesin's, leading to more random motion? This would likely be lots of speculation, but it could be cool to look up some papers on kinesin motility and get its crystal structure to do some comparisons.

\subsection{Next Steps}
\subsubsection{Limitations}

-------------------------------------
Talk about the things we \textit{don't} take into account...motor-motor interaction, 2d information, other ATPase nucleotide state, saying certain mechanochemical steps occur ``fast,'' not taking into account all mechanochemical cycle states, making the coiled coil domain rigid even though it may be springy, 2D model...

@@

Computational limitations: Our project is computational, not experimental. Thus the onus is on us to show that our system is not a humongously over-fit model which just happens to reproduce experimental data, but rather a good physical model of dynein which also replicates data.\\
-------------------------------------

\subsubsection{Improvements to model}

\subsubsection{\textit{Experiments to verify our model}}
Talk about how FRET could be used to verify our model. We have domain distance info over long timescales in our model - this is something we could compare to a FRET experiment exploring the distance between domains in dynein.\\

@@

Calorimetry could get Gibb's energy of binding if you froze the motor in onebound using vanadium? Maybe...\\

\section{Conclusion}
Does anything actually go here?
